\documentclass[reqno,11pt]{article} 

\usepackage{amsmath,amsthm,amssymb,amscd}
\usepackage{url}
\usepackage{dsfont}
\usepackage{mathabx}

\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
columns=flexible,
breaklines=true,
extendedchars=true,
literate={•}{$\bullet$}1 {▄}{$\blacksquare$}1 {□}{$\square$}1
}

\usepackage{url}
\usepackage{graphicx}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}{Definition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{prop}{Proposition}[section]
\newtheorem{conj}{Conjecture}[section]
\newtheorem{claim}{Claim}[section]
\newtheorem{procedure}{Procedure}[section]

\theoremstyle{remark}
\newtheorem{problem}{Problem Statement}[section]
\newtheorem{example}{Example}[section]


\usepackage[top=0.5in,bottom=0.65in,left=0.75in,right=0.75in]{geometry} 
\usepackage[square,sort,comma,numbers]{natbib}

\DeclareMathOperator{\Int}{int}

\newcommand{\PP}[1]{\ensuremath{\mathbb{P}\left(#1\right)}} 
\newcommand{\Iverson}[1]{\ensuremath{\left[#1\right]_{\delta}}}
\newcommand{\Floor}[2]{\ensuremath{\left\lfloor \frac{#1}{#2} \right\rfloor}}

\title{A recent open source embedded implementation of 
       the DESFire specification designed for on-the-fly logging with 
       NFC based systems}
\author{Maxie Dion Schmidt} 
\date{\today}

\setlength{\parskip}{0.35em}
\setlength{\parindent}{0in}

\usepackage{tocloft}
\setlength{\cftsecindent}{0.25em}
\renewcommand{\numberline}[1]{#1~}
\newcommand{\xmark}{\ensuremath{\mathcal{X}}}

\UseRawInputEncoding

\begin{document}

\maketitle 
\medskip\hrule\medskip 

\begin{abstract}
\noindent
Near Field Communication (NFC) is a protocol that offers short-distance wireless 
communication within a proximity of typically less than 10 centimeters. 
Embedded NFC tags are common in applications like physical authentication with door readers, university ID cards, 
bus passes, to exchange credentials 
renting bikes or motorized scooters, and to charge limited credit transactions to vending machines 
and other virtual payment kiosks. 
The Chameleon Mini is a portable device that interfaces with the NFC protocol over RFID. 
This device is designed to facilitate on-the-fly logging of data exchanges between 
contactless cards and 
tag readers operating over NFC in the high-frequency 13.56MHz band. It is an indispensible tool 
for researchers, reverse engineers and system penetration testers who 
perform security analysis over the protocol.
The Chameleon Mini also supports emulation of many contactless card types over NFC that 
are enabled by contributions to its open source embedded firmware. 

The ability to interface and log low-level exchanges with the popular Mifare DESFire tag type 
namufactured by Phillips and NXP on the Chameleon Mini is a useful feature to RFID 
researchers that has been missing from the firmware for many years. 
In 2020, we set out to offer a fully functional open source implementation 
to that adds a frequently requested interface to the Chameleon Mini RevG firmware 
that supports the complex and proprietary DESFire tag command set. 
In this technical presentation, we describe the technologies utilized, applications of this work, 
and describe the challenges of the low-level implementation of the embedded software. 
Updates to this software project are supported by university COVID-19 relief funding 
at Georgia Tech over the Spring of 2022.

\bigskip\noindent
\textbf{Keywords:} 
{\it 
Near field communication, NFC technology, Chameleon Mini, 
contactless smartcards, open source software, DESFire command set, 
RFID cryptographic protocols, embedded systems firmware, reverse engineering.
}

%\bigskip\noindent
%\textbf{A few relevant favorite quotes on software from the conference proceedings article:} \\
%``\emph{That brings me to the most important piece of advice that I can give to all of you: 
%      if you've got a good idea, and it's a contribution, I want you to go ahead and DO IT. 
%	It is much easier to apologize than it is to get permission.}'' -- Grace Hopper \\[0.25cm] 
%``\emph{I think a lot of the basis of the open source movement comes from 
%	procrastinating students.}'' -- Andrew Tridgell \\[0.25cm] 
%``\emph{Life would be much easier if I had the source code.}'' -- Anonymous 

\end{abstract}

\end{document}
