\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\setlength{\parskip}{1em}
\pagestyle{empty}

\begin{document}

\noindent
%Name:\underline{~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~}
MATH1552 Summer 2020
\hspace{2.2cm}
%\noindent
Worksheet 3 Summer
\hspace{2cm} Integral Calculus

\vspace{2mm}
%\hline


\begin{enumerate}
 \item   (Applying the Definite Integral ) A marketing company is trying a new campaign. The
campaign lasts for three weeks, and during this time, the company finds that it gains
customers as a function of time according to the formula:
$$C(t)=7t-4t^2$$
where $t$ is time in weeks and the number of customers is given in thousands.

Using the following form of the definite integral,
$$\int_{a}^{b}f(t)dt=\lim_{n\rightarrow \infty}\frac{b-a}{n}\sum_{i=1}^n f(a+\frac{(b-a)i}{n})$$
calculate the average number of customers gained during the three-week campaign.

Also compute the average number of customers using the form
$$\int_{a}^{b}f(t)dt=\lim_{n\rightarrow \infty}\frac{b-a}{n}\sum_{i=1}^n f(a+\frac{(b-a)(i-1)}{n})$$
Compare the results. What can you confirm from this comparison?



\item Explain why the following property is true:
$$\left\vert\int_{a}^{b}f(t)dt\right\vert\leq \int_{a}^b |f(t)|dt$$
Can you find an example where the inequality is strict?


\item Determine if each statement below is true or false.

	\begin{enumerate}
	\item We always set $x_i$ to be the right-hand endpoint of the $i$th interval.

	\item $$\sum_{i=1}^n i^3=\left(\frac{n(n+1)}{2}\right)^2$$

	\item If $f(x)\geq 0$ on $[a,b]$, then $\int_{a}^b f(t)dt$ represents the total area bounded by $f$, $x=a$, $x=b$ and the $x$-axis.
	\end{enumerate}
\end{enumerate}

\end{document}