\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fullpage}
\setlength{\parskip}{1em}
\pagestyle{empty}

\begin{document}

\vskip 1in
\begin{center}
     {\LARGE 
          Math 1552, Integral Calculus, Summer 2020 \\ 
          Review for Quiz 1
     }
\end{center}
\vskip 0.25in

\bigskip\hrule\bigskip

\begin{itemize}
     \item The first quiz covers the material so far \underline{\emph{through}} integration by substitution. 
     \item Make sure that you have \emph{Honorlock} setup on your computer well in advance of your 
           Studio section on Thursday! 
     \item The quiz will take place \emph{synchronously} at 11:55AM during the last 20 minutes of studio. 
           Be prepared to attend studio and work problems with your TA before the quiz from 11AM-11:54AM. 
     \item NO notes and NO calculators are allowed on the quiz!
     \item See examples of the quiz format at the end of this review sheet.
     \item This review sheet is NOT comprehensive -- see your lecture notes and studio worksheets to make 
           sure you study all of the problem types we may ask you about on the quiz.
\end{itemize}

\bigskip\hrule\bigskip

\newpage
\section{Review problems}

\subsection{General comprehension}

\begin{itemize}
     \item Explain why 
           \[
           - \int_a^b |f(x)| dx \leq \left\lvert \int_a^b f(x) dx \right\rvert \leq 
                \int_a^b |f(x)| dx. 
           \]
     \item Suppose that $\sum\limits_{k=1}^n a_k = 11$ and $\sum\limits_{k=1}^n b_k = 6$. 
           Find the value of the sum $\sum\limits_{k=1}^n \left(2a_k + 3b_k\right)$. 
     \item Which of the following functions are even? Which are odd? \emph{(Why?)} 
           \[
           \pm x, x^2, x^3, x^n; \sin x, \cos x, \tan x, \sec x; 
           \]
           \[
           \frac{x^5+2x^3+x}{(x^2+1)^3}, \frac{x^5+2x^3+1}{(x^2+1)^2}, 
           \frac{x^5+2x^3+x}{(1-x)^3}, \frac{x^5+2x^3+x}{(1-x)^6}
           \]
\end{itemize}

\subsection{Riemann sums and the definite integral}

\begin{itemize}
     \item Give an example of why the inequality $L_f < \int_a^b f(x) dx < U_f$ is \emph{FALSE}. 
     \item Approximate the area $\int_{-1}^{3} (x^3+4) dx$ using 
           \begin{enumerate}
           \item $L_f$ with $n = 4$ rectangles; 
           \item $U_f$ using $n = 4$ rectangles; 
           \item $M_f$ using $n = 2$ rectangles. 
           \end{enumerate}
     \item Evaluate the definite integral 
           \[
           \int_2^{12} (x-2)^4 dx, 
           \]
           using \emph{Riemann sums}. Justify all relevant steps in your solution. 
           Check your answer using the FTC-based methods we have seen to evaluate the 
           integral. \\ 
           \textbf{\underline{Hint}:} Note that for all positive integers $n \geq 1$, 
           we have the formula 
           \[
           \sum_{k=1}^{n} k^4 = \frac{n}{30} (n+1) (2n+1) (3n^2+3n-1). 
           \]
\end{itemize}

\subsection{Antiderivatives and the FTC} 

\begin{itemize}
     \item Recall the antiderivative formulas you need to memorize. 
     \item Recall the FTC (both versions and the chain rule variant from lecture). 
     \item Recall the MVT for integrals. 
     \item Find $F^{\prime}(2)$ if 
           \[
           F(x) = \int_{\frac{8}{x}}^{x^2} \left(\frac{t}{1-\sqrt{t}}\right) dt. 
      \]
     \item Evaluate: $\int\limits \left(\sqrt{x} - \frac{1}{x}\right)^3 dx$. 
     \item Evaluate: $\int\limits \left(\frac{2}{3x} - \frac{1}{\sqrt{16-x^2}}\right) dx$.  
     \item Evaluate: $\int\limits_0^1 \left[8^{-2x} + e^{-3x}\right] dx$. 
     \item Evaluate: $\int\limits_1^2 \frac{3x-5}{x^3} dx$. 
     \item Evaluate: $\int\limits_2^5 (2-x)(x-5) dx$. 
     \item \textbf{(Harder -- fair game!)} 
           Evaluate the following integral: 
           \[
                \int_{-1}^{1} \frac{2x^9 + 3x^5 + 4x^4 + 8x^2 + 4}{(1+x^2)^3} dx. 
           \]
           \emph{Explain why your solution is correct.} 
\end{itemize}

\subsection{Integration by substitution}

\begin{itemize}
     \item Evaluate: $\int\limits \frac{\tan\left(x^{1/3}\right)}{x^{2/3}} dx$. 
     \item Evaluate: $\int\limits_{-\frac{\pi}{6}}^{\frac{2\pi}{3}} x^7 \sec^2\left(x^8\right)$. 
     \item Evaluate: $\int\limits_0^1\left(\frac{e^{\sqrt{5}} + x^{\sqrt{5}}}{\sqrt{x}}\right) dx$. 
\end{itemize}

\newpage
\section{Examples of multiple choice type quiz questions}

\subsection*{Sample question 1.}

Suppose that we are asked to evaluate the following indefinite integral:
\[
\int \frac{dx}{1+x^6}.
\]
Which of the following answers is correct?
\begin{itemize}
\item[(A)] We can evaluate it directly
\item[(B)] Evaluate after the u-sub $u=x^3, du=3x^2dx$ 
\item[(C)] Evaluate after the u-sub $u=x^6, du=5x^5dx$
\item[(D)] We do not know of an elementary solution to this problem (yet)
\end{itemize}

\subsection*{Sample question 2.}

Suppose that we are asked to evaluate the following indefinite integral:
\[
I = \int \frac{x^2}{1+x^6} dx.
\]
Which of the following is an accurate formula for $I$?
\begin{itemize}
\item[(A)] $\tan^{-1}(x^2) + C$
\item[(B)] $\ln(1+x^6) + C$ 
\item[(C)] $\frac{6x^5}{(1+x^6)^2}$
\item[(D)] $\frac{1}{3}\tan^{-1}(x^3) + C$
\item[(E)] We do not know of an elementary solution to this problem (yet)
\end{itemize}





\end{document}
